---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# add2evaluation

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/156731270.svg)](https://zenodo.org/badge/latestdoi/156731270)
<!-- badges: end -->

The goal of add2evaluation is to 
help save time to train model and get prediction in this [contest](www.dcjingsai.com/common/cmpt/国能日新光伏功率预测大赛_竞赛信息.html).
Now I post a discussion [here](http://www.dcjingsai.com/common/bbs/topicDetails.html?tid=2515).

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaxiangBU/add2evaluation")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(add2evaluation)
library(dplyr)
library(ggplot2)
## basic example code
```

See the vignettes.

```{r}
lift_chart(add2evaluation::df, bin_number = 10)
```


## Citations

```{r include=FALSE}
citations <- add2pkg::add_zenodo_citation("README.Rmd")
```

```{r echo=FALSE, results='asis'}
cat(citations$Cite)
```

```{r echo=FALSE, results='asis'}
cat(paste0("```BibTex\n",citations$BibTex,"\n```"))
```

```{r echo=FALSE, results='asis'}
cat(citations$Comments)
```

***

`r add2pkg::add_disclaimer("Jiaxiang Li")`
