---
title: "Get the prediction of test set"
author: "Jiaixang Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Assume we have 

1. test dataset `test`
1. model `xgb_base` which is a xgboost model
1. we want to save it in the directory `data` with name `my_pred.csv`

```{r eval=F}
phv_pred(test,xgb_base,dir='data',output_name='my_pred.csv')
```

***

The official target metric on the [site](http://www.dcjingsai.com/common/cmpt/%E5%9B%BD%E8%83%BD%E6%97%A5%E6%96%B0%E5%85%89%E4%BC%8F%E5%8A%9F%E7%8E%87%E9%A2%84%E6%B5%8B%E5%A4%A7%E8%B5%9B_%E7%AB%9E%E8%B5%9B%E4%BF%A1%E6%81%AF.html) is not usual, thus here is the function I wrap the metric into.

Assume you finish your model and get four coloumn in dataset `dataset`,

1. `id` is the id of the phv machine
1. `t` is time to record every y and x variables
1. `p` is the real power, in this contest, it is the target we want to predict.
1. `phat` is the predicted power, we want it to approach the real one.

```{r}
library(add2evaluation)
data(dataset)
library(lubridate)
library(psych)
library(tidyverse)
dataset %>% 
    describe()
phv_metric(
    id = dataset$short_name
    ,t = dataset$t
    ,y = dataset$p
    ,yhat = dataset$phat
)
```
